---
title: "Replicating the Analysis of Effects of Hurricane Disturbance on Stream Water Concentrations in Bisley, Puetro Rico Streams Before and After Hurricane Hugo"
author: "Rachel Miller"
format: html
---

## Background
The aim of this project is to replicate Figure 3 from Schaefer et al. (2000), displaying the concentration of five different ions in Bisley, Puetro Rico streams before and after Hurricane Hugo.


## Data
```{r}
#| output: false
library(tidyverse)
clean_data <- read_csv("../output/clean_data.csv")
```

The raw data for this project was sourced from [EDI Data Portal](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-luq.20.4923064), and is stored in the data folder. The following files were read to import data for the four relevant sites, and filtered to the years 1986 to 1995:

RioMameyesPuenteRoto.csv

QuebradaCuenca1-Bisley.csv

QuebradaCuenca2-Bisley.csv

QuebradaCuenca3-Bisley.csv


## Methods
The 9-week moving averages of potassium, nitrate-N, magnesium, calcium, and ammonium-N were calculated for four sites representing Bisley. Puertro Rico streams before and after Hurricane Hugo. 


## Results
```{r}
#| echo: false
#| warning: false
ggplot(clean_data,
    mapping = aes(
      x = window_start, 
      y = Concentration,
      linetype = Site
    )
  ) + geom_line() +
  facet_wrap("Ion", scales = "free", ncol = 1, strip.position = "left") +
  geom_vline(xintercept = ymd('1989-09-17'), linetype = "dashed") +
  labs(title = "Concentrations in Bisley, Puerto Rico Streams before and after Hurricane Hugo", x = "Years", y = "Concentration of Ions")

```